A lottery model of density-dependent selection

### 2017-10-13 manuscript.tex
latest

>>>>

Selection has two broadly different connotations, which both appear in the simplest models of evolution. The first is that if one genotype grows faster than another, its frequency will increase. Mathematically, if one genotype's abundance increases at a constant per-capita rate $r_1$, and another at $r_2$, then the frequency of the first $p_1$ changes at rate $(r_1-r_2)p_1 p_2$. Here $s=r_1-r_2$ is the ``selection coefficient''. The second is directly phrased in terms of genotypic frequencies. Two genotypes are assigned relative fitnesss $w_1$ and $w_2$ respectively, and then $p_1$ changes at rate $(w_1-w_2)/\overline{w} p_1 p_2$, where $\overline{w}=w_1p_1+w_2p_2$ is mean relative fitness. While this formulation is agnostic about population size $N$, it is often assumed that $N$ is constant. Thus, in the first connotation, selection is simply differential growth, and does not require interactions between genotypes. The second, on the other hand, connotes the displacement of one genotypes by another, which is intimately connected to the ecological concept of competition \cite{gill_1974}.

The existence of these two different forms of selection was perceived long ago by MacArthur in his $r$/$K$ scheme \citep{macarthur_1962,macarthur_1967}, and before that by Kostitzin \cite{kostitzin_book}.
